Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-09-19 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Upcoming presentation templates

---
title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
subtitle: MRC Centre for Global Infectious Disease Analysis Seminars
author: Adam Howes
institute: Imperial College London
date: May 2022
bibliography: citations.bib
header-includes:
  - \widowpenalties 1 150
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

>>>>

---
title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
subtitle: Centre for Global Health Research, UToronto
author: Adam Howes
institute: Imperial College London
date: May 2022
bibliography: citations.bib
header-includes:
  - \widowpenalties 1 150
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---
